### 2025-01-09 paper/icml25/first/sects/related.tex
minor on related

\paragraph{Multi-Agent Reinforcement Learning}
Multi-Agent Reinforcement Learning (MARL) is a subfield of reinforcement learning that focuses on learning policies for multiple agents that interact with each other~\cite{albrecht2024multi}. 
This field has a wide range of applications, 
including robotics~\cite{DBLP:journals/air/ChungFYN24}, 
traffic control~\cite{DBLP:journals/tits/ChuWCL20}, 
and game playing~\cite{DBLP:conf/iclr/BakerKMWPMM20,jaderberg2019human}, 
and involves different types of agents such as cooperative~\cite{DBLP:journals/corr/abs-2312-05162}, competitive, and mixed. 
In this paper, we primarily focus on cooperative multi-agent scenarios, 
where agents need to collaborate to achieve a common goal. 
Prominent works in this area include extensions of single-agent algorithms to multi-agent settings, 
such as MADDPG~\cite{DBLP:conf/nips/LoweWTHAM17} and MAPPO~\cite{DBLP:conf/nips/YuVVGWBW22}, 
as well as novel solutions to unique challenges in multi-agent settings. Examples of these solutions are COMA~\cite{DBLP:conf/aaai/FoersterFANW18} for multi-agent credit assignment, 
QMIX~\cite{DBLP:conf/icml/RashidSWFFW18} for coordination in cooperative multi-agent settings, 
and Mean Field MARL~\cite{DBLP:conf/icml/YangLLZZW18} for handling a large number of agents.

>>>>

\paragraph{Multi-Agent Reinforcement Learning}
Multi-Agent Reinforcement Learning (MARL) is a subfield of reinforcement learning that focuses on learning policies for multiple agents that interact with each other~\cite{albrecht2024multi}. 
This field has a wide range of applications, 
including robotics~\cite{DBLP:journals/air/ChungFYN24}, 
traffic control~\cite{DBLP:journals/tits/ChuWCL20}, 
and game playing~\cite{DBLP:conf/iclr/BakerKMWPMM20,jaderberg2019human}, 
and involves different types of agents such as cooperative, competitive, and mixed. 
In this paper, we primarily focus on cooperative multi-agent scenarios, 
where agents need to collaborate to achieve a common goal. 
Prominent works in this area include extensions of single-agent algorithms to multi-agent settings, 
such as MADDPG~\cite{DBLP:conf/nips/LoweWTHAM17} and MAPPO~\cite{DBLP:conf/nips/YuVVGWBW22}, 
as well as novel solutions to unique challenges in multi-agent settings. Examples of these solutions are COMA~\cite{DBLP:conf/aaai/FoersterFANW18} for multi-agent credit assignment, 
QMIX~\cite{DBLP:conf/icml/RashidSWFFW18} for coordination in cooperative multi-agent settings, 
and Mean Field MARL~\cite{DBLP:conf/icml/YangLLZZW18} for handling a large number of agents.
